---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(palmerpenguins)
library(urbanC)
```

## Overview of package
The name of the package is **urbanC** and contains the palette *warnCrush* which has 8 colours. The goal of the package is to introduce the urban modern city life colours to R which give a soothing effect.

The colours of the *warmCrush* palette are displayed below:

```{r, include=FALSE}
warmCrush_pal()(6)
```

```{r pie, echo=FALSE, warning=FALSE, message=FALSE}
pal <- warmCrush_pal()(8)
par(mar = rep(0, 4))
pie(rep(1, length(pal)), col = pal)

```

## Usage

```{r, finding_data, include=FALSE}
data(package = 'palmerpenguins')
```

### Discrete Values plot (using colour/color)

#### use **scale_colour_warmCrush_d()** or **scale_color_warmCrush_d()**

```{r, include=FALSE}
penguins <- penguins %>% na.omit()
```

```{r discrete1, out.width='60%', fig.width=4, fig.length=8}
#'colour' or 'color' both can be used.
ggplot(penguins, aes(x=year, y= bill_length_mm, colour = island)) +
  geom_bar(stat = "identity") +
  labs(title = "The length of bills for penguins")+
  ylab("bill length")+
  scale_colour_warmCrush_d()
```

### Discrete Values plot (using fill and direction)

```{r fill, out.width='60%', fig.width=4, fig.length=8}
ggplot(penguins, aes(x=year, y= bill_length_mm, fill = island)) +
  geom_bar(stat = "identity") +
  labs(title = "The length of bills for penguins")+
  ylab("bill length")+
  scale_fill_warmCrush_d(direction = -1)
```

### Continuous Values plot (using colour/color)

```{r continuous,  out.width='60%', fig.width=4, fig.length=8}
#'colour' or 'color' both can be used.
ggplot(penguins, aes(x=flipper_length_mm, y= body_mass_g, colour = bill_length_mm)) +
  geom_point()+
    labs(title = "Correlation between bill and flipper length")+
  ylab("bill length")+
  xlab("flipper length")+
  scale_colour_warmCrush_seq_c()

```

